Resource Use and the Value-Productivity Tradeoff in Australian Winegrowing Regions

### 2023-06-29 article.tex
Fixed introduction and start of methods.

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant quality verses quantity of crops produced. This dilemma exists across agriculture, sharing fundemental considerations such as water and nitrogen input 
\citep{abadCoverCropsViticulture2021}

\cite{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. 
\citet{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}.

Within viticulture (the cultivation of grapes for wine production) quality is driven by its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.

In this analysis we observe relationships between quantity and quality through the use of linear models. Quality can be defined in a variety of ways for grapes, such as *. For the purpose of this study quality was defined by the financial value of grapes per tonne; this was due to varying differences in defining quality between grape varietals.

An extensive amount of research into a variety of factor's effect on grape quality and yield exists. Due to the lack of long-term and in-depth data sources, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insight at a large scale across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.

\section{Methods}
We created four linear models to explore the relationships between resource use and vineyard outputs (see table 1). The models looked at the value and quantity of grapes produced by vineyards, as a total and as a scale of area harvested. We compared values to observe how economies of scale affect the use of resources.

@@

\subsection{Data}
The data used in this analysis was provided by Sustainable Winegrowing Australia, Australia's national wine industry sustainability program. Sustainable winegrowing Australia aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by Sustainable Winegrowing Australia is entered manually by winegrowers using a web based interface; with some fields being optional. Two subsets of this data were defined by vineyards that recorded values for average price of grape sales per tonne, and vineyards who did not. Both subsets contained: region, harvest year, yield, area harvested, water used and fuel used (in litres for diesel, petrol, biodiesel and LPG). To enable comparisons, total fuel was converted to amount of carbon emissions in metric tons.

@@

Data was limited to samples that had recorded values for variables used (see Table 1). After reviewing correlation coefficients the data was logarithmically transformed, centred and scaled by standard deviation. Two values for average sale price were removed from the dataset, due to a recording of \$1. Unreported values for average prices per tonne were filled in using regional averages taken from Wine Australia's annual reports, where they were available \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2012,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.

>>>>

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield verses quality produced. This dilemma exists across agriculture within shared fundamental considerations such as water and nitrogen inputs \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. Within viticulture (the cultivation of grapes for wine production) quality is driven by its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.
\newline
In this analysis we observe relationships between yield and quality through the use of linear models. Quality can be defined in a variety of ways, for example analysing grapes' aroma, chemical composition and color. For the purpose of this study, quality was defined by winegrape crops' financial value per tonne. This definition assumes due diligence on the side of those that purchased the grapes; where market value of grapes heavily relies on grape quality \citep{yeggeInfluenceSensoryNonsensory2001}. Wine Australia also links grape quality to price per tonne, by explicitly defining grape quality within discrete price brackets.
\newline
An extensive amount of research into a variety of factors' effect on grape quality and yield exists.
% there needs to be references if there is extensive research
Due to the lack of long-term and in-depth data, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.
\newline
We aim to use this broad dataset to confirm the existence of a yield verse quality trade off within Australian winegrowing; one not prior confirmed explicitly across such extensive diversities.
% you require a reference here
In achieving this, the context of how resource use relates to yield and quality will also be described. We link these relations to the potential for improvement through decision-making processes, and highlight that the way moving forward will require the optimisation of this process. The practical addition of these aims is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality.
\section{Methods}
We created four linear models to explore relationships between resources used and vineyard outputs (see Table 1). The response variables of the models were yield and quality, with yield being measured in tonnes and quality being the product of yield and the average sale price per tonne. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

\subsection{Data}
Data used in this analysis was provided by Sustainable Winegrowing Australia, Australia's national wine industry sustainability program; which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by Sustainable Winegrowing Australia is entered manually by winegrowers using a web based interface, with some fields being optional. Two subsets of this data were defined through vineyards which did not record average price of sale per tonne, and vineyards which did or which were in a region of known average price. Vineyards which did not record a value for average price of sale per tonne but were within regions with a recorded average price of sale per tonne by Wine Australia were filled in using this regional average. Both subsets contained: region, harvest year, yield, area harvested, water used and fuel used (diesel, petrol, biodiesel and LPG). To enable comparisons, total fuel was converted to equivalent carbon emissions in metric tons.

@@

Data was limited to samples that had recorded values for variables used (see Table 1). After reviewing correlation coefficients the data was logarithmically transformed, centred and scaled by standard deviation. Two values for average sale price were removed from the dataset, due to a recording of \$1. 
% \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2012,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.
